paper

### 2021-10-08 paper.Rmd
kl

```{r}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(ggtext)
library(lme4)
library(tidymodels)
library(lmerTest)
library(ggthemes)
library(ggrepel)
```

@@

@@

@@

@@

@@

```{r}
epred_wt %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig1

ggsave("figures/Figure 2.png", width = 8, height = 4)
```

@@

```{r}
new_dt %>% 
  group_by(herbicide) %>% 
  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
            counts = mean(counts_m2, na.rm = TRUE))
```

```{r}
epred4 <- emmeans(model4, "herbicide", epred = TRUE,
                  #cont="pairwise"
                  )
epred4
```

@@

```{r}
epred4_wt %>% 
  mutate(herbicide = fct_relevel(herbicide,
                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
                                            "glufosinate + imazethapyr", 
                                            "glufosinate + *S*-metolachlor",
                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
                                            "glufosinate + fomesafen", 
                                            "glufosinate + fomesafen + acetochlor",
                                            "glufosinate + fomesafen + *S*-metolachlor"))) -> epred4_wt1
```
```{r}
epred4_wt1 %>%
  mutate(herbicide = fct_relevel(herbicide,
                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
                                            "glufosinate + imazethapyr", 
                                            "glufosinate + *S*-metolachlor",
                                            "glufosinate + pyroxasulfone", 
                                            "glufosinate + acetochlor", "glufosinate + fomesafen",
                                            "glufosinate + fomesafen + acetochlor",
                                            "glufosinate + fomesafen + *S*-metolachlor"))) -> epred4_wt1
```

```{r}
epred4_wt %>%
  ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 size = 1.2) +
  coord_flip() +
  geom_text_repel(aes(label = round(emmean,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
  scale_color_calc() +
  scale_y_continuous(limits = c(0,75), breaks = seq(0, 75, 15)) +
  labs(x = NULL, y = expression(paste("Soybean yield (bu acre"^"-1",")"))) +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig2

@@

>>>>

```{r}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(ggtext)
library(lme4)
library(tidymodels)
library(lmerTest)
library(ggthemes)
library(ggrepel)
library(tidytext)
```

@@

```{r}
new_dt |> 
  ggplot(aes(x = herbicide, y = waterhempcontrol_harvest)) +
  geom_boxplot() +
  coord_flip() +
  geom_jitter() +
  facet_grid(year ~ location)
```

```{r}
new_dt |> 
  ggplot(aes(x = herbicide, y = waterhempcontrol_harvest)) +
  geom_boxplot() +
  coord_flip() +
  geom_jitter() +
  facet_grid(year ~ location)
```

@@

```{r}
epred1_1 %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred1_11
```

```{r}
epred1_11 |> 
  mutate(herbicide = fct_relevel(herbicide,
                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
                                            "glufosinate + imazethapyr", 
                                            "glufosinate + *S*-metolachlor",
                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
                                            "glufosinate + fomesafen + acetochlor",
                                            "glufosinate + fomesafen + *S*-metolachlor",
                                            "glufosinate + fomesafen"))) |> 
  mutate(emmean = round(emmean, 2)) -> epred1_111
```

```{r}
epred1_111 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        axis.title.x = element_blank(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig1

ggsave("figures/Figure 2.png", width = 5, height = 4)
```

@@

```{r}
epred2_2 %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred2_22
```

```{r}
epred2_22|> 
  mutate(herbicide = fct_relevel(herbicide,
                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
                                            "glufosinate + imazethapyr", 
                                            "glufosinate + *S*-metolachlor",
                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
                                            "glufosinate + fomesafen + acetochlor",
                                            "glufosinate + fomesafen + *S*-metolachlor",
                                            "glufosinate + fomesafen"))) |> 
  mutate(emmean = round(emmean, 2)) -> epred2_222
```

```{r}
epred2_222 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        axis.title.x = element_blank(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig2

ggsave("figures/Figure 22.png", width = 5, height = 4)
```

@@

```{r}
epred5 %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred55
```

```{r}
epred55 |> 
  mutate(herbicide = fct_relevel(herbicide,
                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
                                            "glufosinate + imazethapyr", 
                                            "glufosinate + *S*-metolachlor",
                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
                                            "glufosinate + fomesafen + acetochlor",
                                            "glufosinate + fomesafen + *S*-metolachlor",
                                            "glufosinate + fomesafen"))) |> 
  mutate(emmean = round(emmean, 2)) -> epred555
```

```{r}
epred555 %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig3

#ggsave("figures/Figure 222.png", width = 5, height = 4)
```

```{r}
library(patchwork)
```

```{r}
fig1 / fig2 / fig3 +
  plot_annotation(tag_levels = 'A')

ggsave("figures/Figure 2.png", width = 6, height = 12)
```

@@

```{r}
epred_wt %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
#  scale_color_brewer(palette = "Set1") +
  scale_color_calc() +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11, face = "bold"),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333"))

#ggsave("figures/Figure 2.png", width = 9, height = 4)
```

@@

@@

```{r}
epred4_wt %>% 
  mutate(herbicide = fct_relevel(herbicide,
                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
                                            "glufosinate + imazethapyr", 
                                            "glufosinate + *S*-metolachlor",
                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
                                            "glufosinate + fomesafen", 
                                            "glufosinate + fomesafen + acetochlor",
                                            "glufosinate + fomesafen + *S*-metolachlor"))) -> epred4_wt1
```

```{r}
epred4_wt1 %>%
  ggplot(aes(x = fct_reorder(herbicide, emmean),
           y = emmean, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 size = 1.2) +
  coord_flip() +
  geom_text_repel(aes(label = round(emmean,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_nudge_repel(x = 0.3),
                    seed = 465) +
  scale_color_calc() +
  scale_y_continuous(limits = c(0,75), breaks = seq(0, 75, 15)) +
  labs(x = NULL, y = expression(paste("Soybean yield (bu acre"^"-1",")"))) +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none",
        plot.background = element_rect(fill = "#F5F5F5"),
        panel.background = element_rect(fill = "#F5F5F5"),
        axis.text = element_markdown(color = "#333333")) -> fig2

@@

## Weed density

```{r}
new_dt |> 
  ungroup() |> 
  dplyr::select(location, year, herbicide, rep, counts_m2) |> 
  filter(!is.na(counts_m2)) -> density
```

```{r}
model6 <- brm(counts_m2 ~ herbicide +
                (1|rep/location), 
                  family = poisson(),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 2, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
epred6 <- emmeans(model6, "herbicide", epred = TRUE,
                  #cont="pairwise"
                  )
epred6
```

```{r}
density_main <- pairs(emmeans(model6, ~ herbicide))

describe_posterior(density_main,
                   centrality = "median", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model6)
```
